Accelerometer-derived ballistocardiogram confirms blue whale (*Balaenoptera musculus*) heart rate during diving bradycardia

### 2021-10-20 analysis/paper/paper.Rmd
Use power spectral density to quantify signal:noise
Former-commit-id: c7c773281971e09c5e41b25c3027a993ef596d4e

---
title: "Something about cetacean heart rates and ballistocardiograms"
author:
  - Max Czapanskiy:
      email: maxczap@stanford.edu
      institute: [SU]
      correspondence: true
  - More Authors:
      email: more@authors.edu
      institute: [UofA]
      correspondence: false
institute:
  - SU: Stanford University
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

# Background

# Methods

# Results

@@

```{r bw-beats}
window = 1.8 # s
bw_elg <- bw180905_53_elg

@@

# foo <- lapply(unique(na.omit(bw_400hz$region_id)), bw_bcg_plot)
```

@@

# Discussion

# Conclusion

>>>>

---
title: "Accelerometer-derived ballistocardiogram confirms blue whale (*Balaenoptera musculus*) heart rate during diving bradycardia"
author:
  - Max Czapanskiy:
      email: maxczap@stanford.edu
      institute: [SU]
      correspondence: true
  - More Authors:
      email: more@authors.edu
      institute: [UofA]
      correspondence: false
institute:
  - SU: Stanford University
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  diving physiology; cardiovascular physiology; accelerometer; bio-logging; marine mammal
---

@@

# Materials and methods

# Results and discussion

@@

```{r bw-beats}
window <- 1.8 # s
bw_elg <- bw180905_53_elg

@@

foo <- lapply(unique(na.omit(bw_400hz$region_id)), bw_bcg_plot)
```

@@
